---
title: "Short Lab 1"
author: "INSERT YOUR NAME HERE"
date: "Due Date Here"
output: html_document
---

<!--- Begin styling code. --->
<style type="text/css">
/* Whole document: */
body{
  font-size: 12pt;
}
h1.title {
  font-size: 38px;
  text-align: center;
}
h4.author {
  font-size: 18px;
  text-align: center;
}
h4.date {
  font-size: 18px;
  text-align: center;
}
</style>
<!--- End styling code. --->

You should edit this .Rmd using RStudio, then click *Knit* in the menu bar of the Source window (above the text of this .Rmd).
Remember, you must submit *both* your .Rmd and the compiled .html in order to receive full credit!

## Part 1. Atomic vectors

**1.** Fill in the code below to assign two numeric variables.

```{r}
# Your code here
```

**2.** Use object type functions to confirm your variables are numeric.

```{r}
# Your code here
```

**3.** Write one line of code that involves an arithmetic operator and both of your variables.

```{r}
# Your code here
```

**4.** Write one line of code that involves a comparison operator, both of your variables, and evaluates to `TRUE`. Add a comment to explain what your code is doing in words.

```{r}
# Your code here
```

## Part 2. Vectors and matrices

**5.** What does the following code do?

```{r, eval = T}
set.seed(456)
```

**6.** Using the code below, we can simulate a vector of Uniform(0,1) random variables and two additional random variables ```y``` and ```z```. What is the difference between ```y``` and ```z```?

```{r, eval = T}
x <- runif(2000)
y <- mean(x < .5)
z <- mean(x)
```

**7.** Construct a 3 by 3 matrix with 1s on the main diagonal and 3s in all other entries.

## Part 3. Some real data

**8.** First, run ```install.packages("moderndive")``` and then the following code. This loads the ```house_prices``` dataset, which contains house sale data for King Country. What time period are these house prices from?

```{r}
library(moderndive)
data("house_prices")
```

**9.** The ```house_prices$bedrooms``` vector contains information on the number of bedrooms in each house. What is the median value? What is the most common value?

```{r}
# Your code here
```

**10.** (Optional) The ```house_prices$bedrooms``` vector contains information on the number of bedrooms in each house. What is the maximum value? Is this realistic? Can you figure out what happened here?